You Draw It': Implementation of visually fitted trends with `r2d3`

### 2022-11-14 revisions/response-to-reviewers.qmd

+ Another comment is that I recommend the authors update figure 2 too (AE commented about figure 1), because the gray text is hard to see. 
  + \response{Figure 2 is a screenshot directly from the New York Times website used to demonstrate the use of the 'You Draw It' feature for interactive reading. While we could try to recreate this image or modify the colors, this changes the actual figure shown to readers in the New York Times.}

+ Also, figures 3 and 6 are difficult to read given there are three subplots. If there is space, perhaps the authors can reconfigure the plots, such as creating two rows (i.e., one plot in one row, and two plots in one row). 
  + \response{Figure 3 was reconstructed to provide the three subplots in vertical order spanning an entire page for better visability. As these subplots have a natural flow, we did not want to interupt this by creating a 2 + 1 subplot figure structure.}
  + \response{Figure 6 was reconstructed to provide a 1 + 2 subplot figure structure, keeping the two predicted plots from different models next to each other in the second row.}

+ Further, please note that all figures should be generated as vector images to ensure they’re high quality for final journal publication.
  + \response{Figure 1, Figure 5, and Figure 6 were generated within R and saved directly to pdf files from within the R environment. We expect these are all vector compatible; please let us know if this isn't sufficient or if we should use a different graphics device.}
  + \response{Figure 2 and Figure 3 were screenshots taken from websites. We zoomed in on a high quality screen and took a screenshot; saved as high resolution png files.}
  + \response{Figure 4 was sketched using an online tool; saving this as an svg changes the appearance of the font type and we would like to keep the sketched font. We saved this at the highest resoultion the tool allowed as a png file.}

<!-- latexdiff C:/Users/erobin17/Documents/publications/2022-sdss-you-draw-it-manuscript/original-2022-sdss-you-draw-it-manuscript.tex C:/Users/erobin17/Documents/publications/2022-sdss-you-draw-it-manuscript/2022-sdss-you-draw-it-manuscript.tex > C:/Users/erobin17/Documents/publications/2022-sdss-you-draw-it-manuscript/diffs1.tex -->

### 2022-11-14 2022-sdss-you-draw-it-manuscript.qmd
revisions 1 done

The 'You Draw It' graphical task presented in this work is an example of an interactive graphic; an interactive graphic is defined as a user-driven direct manipulation of the plot followed by an immediate reaction [@unwin1999requirements; @eick1995high; @becker1987dynamic].
Here we discuss the use of 'You Draw It' as a tool for interactive reading, interactive testing, and interactive teaching as a way to increase user experience and user engagement with data.
The New York Times first introduced the 'You Draw It' feature as a tool for interactive reading.
The inclusion of interactive graphics in news and media have been used to inform readers in efforts to reduce misconceptions and aid in storytelling [@geidner2015role; @george2011interactive; @george2013storytelling].
In our work, we demonstrated the use of the 'You Draw It' method as a tool for interactive testing of graphics.
We collected and compared data from user drawn lines to statistical results in order to understand perceptual biases.
While this work has many possible directions for future work, there is a strong application to extend the 'You Draw It' tool for interactive teaching.
The line of best fit is introduced in secondary schools as a student's first encounter with the concept of statistical association between multiple variables [@casey2016students].
@casey2015examining and @casey2016finding conducted task based interviews to examine student's conceptions of the line of best fit prior to introducing the topic.
The implications of using interactive teaching tools for the line of best fit can help students make connections between the shift in slope and the location of the best fit line [@nagle2017slope].
@casey2015teachers conducted similar task based interviews wish pre-service mathematics teachers in order to understand the effects regarding teacher preparation for the teaching of this topic. 
This demonstrates the use of the 'You Draw It' interactive tool for training purposes both within a classroom setting and for those in the workforce.

>>>>

The 'You Draw It' graphical task presented in this work is an example of an interactive graphic.
<!-- an interactive graphic is defined as a user-driven direct manipulation of the plot followed by an immediate reaction [@unwin1999requirements; @eick1995high; @becker1987dynamic]. -->
Here we discuss the use of 'You Draw It' as a tool for interactive reading, interactive testing, and interactive teaching as a way to increase user experience and user engagement with data.
The New York Times first introduced the 'You Draw It' feature as a tool for interactive reading.
The inclusion of interactive graphics in news and media have been used to inform readers in efforts to reduce misconceptions and aid in storytelling [@geidner2015role; @george2011interactive; @george2013storytelling].
In our work, we demonstrated the use of the 'You Draw It' method as a tool for interactive testing of graphics.
We collected and compared data from user drawn lines to statistical results in order to understand perceptual biases.
While this work has many possible directions for future work, there is a strong application to extend the 'You Draw It' tool for interactive teaching.
The line of best fit is introduced in secondary schools as a student's first encounter with the concept of statistical association between multiple variables [@casey2016students].
@casey2015examining and @casey2016finding conducted task based interviews to examine student's conceptions of the line of best fit prior to introducing the topic.
The implications of using interactive teaching tools for the line of best fit can help students make connections between the shift in slope and the location of the best fit line [@nagle2017slope].
@casey2015teachers conducted similar task based interviews with pre-service mathematics teachers in order to understand the effects regarding teacher preparation for the teaching of this topic. 
This demonstrates the use of the 'You Draw It' interactive tool for training purposes both within a classroom setting and for those in the workforce.
